Litrepl: Literate Paper Processor Promoting Transparency More Than Reproducibility

### 2025-01-01 paper/paper.tex
Update paper

\begin{abstract}
Litrepl is a Python text processor for recognizing and evaluation code sections
in Markdown or LaTeX documents. Litrepl is designed as a middleware aimed at
separating text editors from the programming language interpreter management
logic thus contributing to the diversity of both. In this role, Litrepl can
become a component of modular "UNIX Way" interactive development or typesetting
environments.
\end{abstract}

>>>>

\begin{abstract}
Litrepl is a text processor tool for recognizing and evaluating code sections in
Markdown or LaTeX documents. Litrepl is designed as middleware aimed at
separating text editors from the programming language interpreter management
logic, thus contributing to the diversity of both.
\end{abstract}
